---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
[![Travis-CI Build Status](https://travis-ci.org/chrishaid/deanslistr.svg?branch=master)](https://travis-ci.org/chrishaid/deanslistr)
[![Coverage Status](https://img.shields.io/codecov/c/github/chrishaid/deanslistr/master.svg)](https://codecov.io/github/chrishaid/deanslistr?branch=master)


`deanslistr` is an R package that wraps the DeansList RESTful HTTP API for use in R programming. It is currently under active development by Chris Haid at KIPP Chicago with the hope of releasing it on CRAN. 

## Installation

Installation is easy:
```{r install, eval=TRUE}
if(!require(devtools)) install_packages('devtools')

devtools::install_github('chrishaid/deanslistr')
```

## Basic Usage
Usage is straightforward for version 1 API endpoints.  You simply pass the last portion the endoint path to the `endpoint` paramater of the `deanslist_api()` function, along with your domain and API access key:
```{r v1}
library(deanslistr)

dla_key <- Sys.getenv("KEY_DLA")

x <- deanslist_api(endpoint = 'suspensions',
                   domain = 'dlacademy',
                   key = dla_key)

x
```

Notice that while the `deanslist_api()` will try to coerce nested JSON to a data frame, some fields may be stored as lists (e.g., `Penalties` and `Actions` in the above response). So pay attion to the content that's returned; you might need to do some more munging with something like `tidyr::unnest()`

The remaing beta endpoints are taken processed on a case by case basis and require passing the `endpoint_version = 'beta'` to the `deanslist_api()`:

```{r beta}
x <- deanslist_api(endpoint = 'users',
                   domain = 'dlacademy',
                   key = dla_key,
                   endpoint_version = 'beta')

x
```

## Convenience Wrappers

The package has some convenience functions that wrap `deanslist_api()` for specific endpoints. These wrappers all start with a `get_` prefix.  The first (and curruntly only) wrapper is `get_suspensions`.  The onus for these functions is to facilitate calling `deanslist_api` for multiple schools.  If you have six schools you will need to provide 6 keys to `deanslist_api`, one-at-a-time. the `get_` functions can take take multiple keys via the `key_list` parameter. Better still, you can store keys in `.Renviron` file, which will be sourced when R starts (if saved in a users home directory).  The keys' variables need to fit hte pattern of `DL_KEY_` where the `SCHOOL` bit can be any test string. `get_` wrappers, if not passed a list of keys explicitely, will look to your environment variables for keys stored in the `DL_KEY_` variables and requirest the data from DeansList and (try to) store the returned data as a list of data frames.  This list of data frames is best handled with `purrr` or other `tidyverse` functions. 

```{r eval=FALSE}
x <- get_suspensions(domain = 'dlacademy`)


```





