---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
[![Travis-CI Build Status](https://travis-ci.org/chrishaid/deanslistr.svg?branch=master)](https://travis-ci.org/chrishaid/deanslistr)
[![Coverage Status](https://img.shields.io/codecov/c/github/chrishaid/deanslistr/master.svg)](https://codecov.io/github/chrishaid/deanslistr?branch=master)


`deanslistr` is an R package that wraps the DeansList RESTful HTTP API for use in R programming. It is currently under active development by Chris Haid at KIPP Chicago with the hope of releasing it on CRAN. 

Installation is easy:
```{r install, eval=TRUE}
if(!require(devtools)) install_packages('devtools')

devtools::install_github('chrishaid/deanslistr')
```

Usage is straightforward for version 1 API endpoints.  You simply pass the last portion the endoint path to the `endpoint` paramater of the `deanslist_api()` function, along with your domain and API access key:
```{r v1}
library(deanslistr)

dla_key <- Sys.getenv("KEY_DLA")

x <- deanslist_api(endpoint = 'suspensions',
                   domain = 'dlacademy',
                   key = dla_key)

x
```

Notice that while the `deanslist_api()` will try to coerce nested JSON to a data frame, some fields may be stored as lists (e.g., `Penalties` and `Actions` in the above response). So pay attion to the content that's returned; you might need to do some more munging with something like `tidyr::unnest()`

The remaing beta endpoints are taken processed on a case by case basis and require passing the `endpoint_version = 'beta'` to the `deanslist_api()`:

```{r beta}
x <- deanslist_api(endpoint = 'users',
                   domain = 'dlacademy',
                   key = dla_key,
                   endpoint_version = 'beta')

x
```






